---
title: "P8105_hw5_ykk2116"
author: "Yaa Klu"
date: "11/6/2018"
output: github_document
---

_Loading tidyverse and rvest_

```{r}
library(tidyverse)
library(plotly)
library(rvest)
```


### Problem 1


_Making dataframe containing all file names_

```{r}
allfiles_df = tibble(filepath = list.files("./data/", pattern = "*.csv", full.names = TRUE),
                     filename = basename(filepath))
```


_Function for data_

```{r}
data_reading = function(data){
  
  read_csv(file = data)
}
```


_Iterating and reading in data for each subject, data cleaning_

```{r, message=FALSE}
data_f = allfiles_df %>% mutate(data = purrr::map(allfiles_df$filepath, data_reading)) %>%
  unnest() %>% 
  select(-filepath) %>%
  gather(key = week, value = value, week_1:week_8) %>%
   mutate(id = str_replace(filename, ".csv",""),
         week = as.numeric(str_replace(week, "week_", ""))) %>%
    separate(id, into = c("group", "id"), sep = "_") %>% 
  mutate(id = as.factor(id))  
``` 

_Spaghetti Graph_

```{r}
ggplot(data_f, aes(x = week, y = value, color = id, group = id)) + geom_point() + geom_line() + facet_grid(~group) +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8)) +
  labs(
     title = "Observations from each subject over a period of eight weeks",
    x = "Week",
    y = "Observation Value"
  )
```

_Differences between experimental and control groups_

**Looking at all control subjects as a group, there was no clear trend with time. Overall it seems that there was no difference between observations at week 1 and week 8. In between the 8 weeks there were random increases and decreases among specific subjects. In the experimental arm, there was an increase in the observation value from week 1 to week 8. In between the 8 weeks, there were some ups and downs just as was observed in the control group. To conclude, the values of observation were higher in the experimental arm after 8 weeks, whiles in the control arm, there was no increase**



### Problem 2

_Reading data and creating variable_


```{r}
homicide_data = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv", col_names = TRUE) %>% 
  mutate(city_state = str_c(city, ",", " ", state))
```

_Description of raw data_

**The raw data contains 52,179 homicide records. The data is described by 13 different variables including the race, sex, and age of victims and the date of incident report. It also contains the first and last names of victims and the state and city in which the homicide occured; longitude and latitude information was also collected. The desposition indicates whether the homicide case was closed without any arrest, closed due to arrest or still open with no arrest.**

_Summarizing within cities to obtain the total number of homicides and the number of unsolved homicides_

```{r}
data_summary = homicide_data %>% 
  mutate(disposition = fct_collapse(homicide_data$disposition, "No arrest" = c("Closed without arrest","Open/No arrest"))) %>% group_by(city_state) %>% 
  count(disposition) %>% 
  spread(key = disposition, value = n) %>% 
  janitor::clean_names(dat = .) %>% 
  mutate(total = closed_by_arrest + no_arrest)
```


```{r}
city_baltimore = data_summary %>% filter(city_state == "Baltimore, MD")

baltimore_prop = prop.test(baltimore$no_arrest, baltimore$total) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high) %>% 
  janitor::clean_names(dat = .) %>% 
  knitr::kable()

baltimore_prop



```

 

